\section{Locally Metrizable Spaces}

\begin{df}[Locally Metrizable]
  A space is \emph{locally metrizable} iff every point has a metrizable
  neighbourhood.
\end{df}

\begin{prop}
  Every metrizable space is locally metrizable.
\end{prop}

\begin{proof}
  \pf\ Trivial. \qed
\end{proof}

\begin{cor}
  The space $\mathbb{R}^\omega$ is locally metrizable.
\end{cor}

\begin{prop}
  A compact Hausdorff space is metrizable if and only if it is locally
  metrizable.
\end{prop}

\begin{proof}
  \pf
  \step{<1>1}{\pflet{$X$ be a locally metrizable compact Hausdorff space}}
  \step{<1>2}{$X$ is regular}
  \begin{proof}
    \pf\ Lemma \ref{lm:topology:compact:normal}
  \end{proof}
  \step{<1>3}{$X$ is second countable}
  \begin{proof}
    \step{<2>1}{$\{ U : U \text{ open in } X \text{ and metrizable} \}$ covers
    $X$}
    \step{<2>2}{\pick\ a finite subcover $U_1$, \ldots, $U_n$}
    \step{<2>3}{For $1 \leq i \leq n$, \pick\ a countable basis $\mathcal{B}_i$
    of
    $U_i$}
    \step{<2>4}{$\mathcal{B}_1 \cup \cdots \cup \mathcal{B}_n$ is a basis for
    $X$}
  \end{proof}
  \qedstep
  \begin{proof}
    \pf\ By the Urysohn Metrization Theorem.
  \end{proof}
  \qed
\end{proof}

\begin{cor}
  $\overline{S_\Omega}$ is not locally metrizable.
\end{cor}

\begin{cor}
  The ordered square is not locally metrizable.
\end{cor}

\begin{prop}
  Every subspace of a locally metrizable space is locally metrizable.
\end{prop}

\begin{proof}
  \pf
  \step{<1>1}{\pflet{$X$ be locally metrizable and $Y \subseteq X$}}
  \step{<1>2}{\pflet{$y \in Y$}}
  \step{<1>3}{\pick\ a metrizable neighbourhood $U$ of $y$ in $X$}
  \step{<1>4}{$U \cap Y$ is a metrizable neighbourhood of $y$ in $Y$}
  \qed
\end{proof}

\begin{cor}
  $S_\Omega \times \overline{S_\Omega}$ is not locally metrizable.
\end{cor}

\begin{proof}
  \pf\ It has a subspace homeomorphic to $\overline{S_\Omega}$. \qed
\end{proof}

\begin{prop}[CC]
  Every locally metrizable regular Lindel\"{o}f space is metrizable.
\end{prop}

\begin{proof}
  \pf
  \step{<1>1}{\pflet{$X$ be a locally metrizable regular Lindel\"{o}f space.}}
  \step{<1>2}{Every point in $X$ has an open second countable neighbourhood.}
  \begin{proof}
    \step{<2>1}{\pflet{$x \in X$}}
    \step{<2>2}{\pick\ an open metrizable $U$ containing $x$}
    \begin{proof}
      \pf\ $X$ is locally metrizable (\stepref{<1>1})
    \end{proof}
    \step{<2>3}{\pick\ an open $V$ such that $x \in V \subseteq \overline{V}
    \subseteq
    U$}
    \begin{proof}
      \pf\ Proposition \ref{prop:topology:regular:closure}
    \end{proof}
    \step{<2>4}{$\overline{V}$ is Lindel\"{o}f}
    \begin{proof}
      \pf\ Proposition \ref{prop:topology:Lindelof:subspace}
    \end{proof}
    \step{<2>5}{$\overline{V}$ is second countable}
    \begin{proof}
      \pf\ Proposition \ref{prop:topology:metric:Lindelof_second_countable}
    \end{proof}
  \end{proof}
  \step{<1>3}{\pick\ a countable covering of secound countable open sets
  $\mathcal{U}$}
  \begin{proof}
    \pf\ $X$ is Lindel\"{o}f (\stepref{<1>1})
  \end{proof}
  \step{<1>4}{For $U \in \mathcal{U}$, \pick\ a countable basis $\mathcal{B}_U$}
  \step{<1>5}{$\bigcup_{U \in \mathcal{U}} \mathcal{B}_U$ is a countable basis
  for
  $X$}
  \begin{proof}
    \step{<2>1}{\pflet{$x \in U$ where $U$ is open in $X$}}
    \step{<2>2}{\pick\ $V \in \mathcal{U}$ such that $x \in V$}
    \step{<2>3}{There exists $B \in \mathcal{B}_V$ such that $x \in B \subseteq
    U
    \cap       V$}
  \end{proof}
  \qedstep
  \begin{proof}
    \pf\ By the Urysohn Metrization Theorem.
  \end{proof}
  \qed
\end{proof}

\begin{cor}
  $\mathbb{R}_l$ is not locally metrizable.
\end{cor}

\begin{prop}
  The Sorgenfrey plane is not locally metrizable.
\end{prop}

\begin{proof}
  \pf
  \step{<1>1}{\pflet{$U$ be any neighbourhood of $(0,0)$} \prove{$U$ is not
  Lindel\"{o}f}}
  \step{<1>2}{\pick\ $a > 0$ such that $[0,a)^2 \subseteq U$}
  \step{<1>3}{\pflet{$L = \{ (x, a-x) : 0 < x < a \}$}}
  \step{<1>4}{$L$ is closed in $U$}
  \begin{proof}
    \pf\ By Lemma \ref{lm:closed_sorgenfrey} since $(x,y) \mapsto (x,a+y)$ is
    a homeomorphism of $\mathbb{R}_l^2$ with itself.
  \end{proof}
  \step{<1>5}{\pflet{$\mathcal{U} = \{ U \setminus L \} \cup \{ ([x,b) \times
  [a-x,c)) \cap U : b > a, c > a - x \}$}}
  \step{<1>6}{$\mathcal{U}$ covers $U$}
  \step{<1>7}{No countable subset of $\mathcal{U}$ covers $U$}
  \begin{proof}
    \pf\ Every set of the for $[x,b) \times [a-x,c)$ intersects $L$ in exactly
    one point.
  \end{proof}
  \qed
\end{proof}

\begin{cor}
  The Sorgenfrey plane is not metrizable.
\end{cor}

\begin{prop}
  The space $\mathbb{R}_K$ is locally metrizable.
\end{prop}

\begin{proof}
  \pf\ The set $(-1, 1) - K$ is a metrizable neighbourhood of 0. For any other
  point $p$, pick an open interval around $p$ that does not contain 0. \qed
\end{proof}
\begin{prop}
  The product of two locally metrizable spaces is locally metrizable.
\end{prop}

\begin{proof}
  \pf
  \step{<1>1}{\pflet{$X$ and $Y$ be locally metrizable}}
  \step{<1>2}{\pflet{$(a, b) \in X \times Y$}}
  \step{<1>3}{\pick\ metrizable neighbourhoods $U$ of $a$ and $V$ of $b$}
  \step{<1>4}{$U \times V$ is a metrizable neighbourhood of $(a, b)$.}
  \begin{proof}
    \pf\ By Lemma \ref{lm:topology:metric:product}.
  \end{proof}
  \qed
\end{proof}


\begin{prop}
  The product of two locally metrizable spaces is locally metrizable.
\end{prop}

\begin{proof}
  \pf
  \step{<1>1}{\pflet{$X$ and $Y$ be locally metrizable}}
  \step{<1>2}{\pflet{$(a, b) \in X \times Y$}}
  \step{<1>3}{\pick\ metrizable neighbourhoods $U$ of $a$ and $V$ of $b$}
  \step{<1>4}{$U \times V$ is a metrizable neighbourhood of $(a, b)$.}
  \begin{proof}
    \pf\ By Lemma \ref{lm:topology:metric:product}.
  \end{proof}
  \qed
\end{proof}

\begin{prop}
  The space $\mathbb{R}_K^\omega$ is not locally metrizable.
\end{prop}

\begin{proof}
  \pf\ If it were, then there would be a basic open set $\prod_n U_n$ that is metrizable, but then $\mathbb{R}_K$ would be metrizable as it is homeomorphic to a subspace of $\prod_n U_n$. \qed
\end{proof}

\begin{cor}
  The product of a countable family of locally metrizable spaces is not necessarily locally metrizable.
\end{cor}

\begin{prop}
  The continuous image of a locally metrizable space is not necessarily locally metrizable.
\end{prop}

\begin{proof}
  \pf\ The identity map from the discrete two-point space to the indiscrete two-point space is continuous. \qed
\end{proof}
